Challenges in Developing Great MCQMC Software

### 2022-07-13 MCQMC_2022_ChallengesDevelopSoftware.tex
Updates from Overleaf
Office Computer Updates

\section{Background}

@@

>>>>

\section{Introduction}

@@

\begin{frame}{Why Do We Need Software?}
\end{frame}

\begin{frame}{Selective History of MC\textbf{QMC} Software}
	\vspace{-6ex}
	\begin{itemize}
		\item \textcite{LEc2017a} provides a history of \alert{random number generation}
		\item Notorious \alert{\texttt{randu}} from the 1960s \parencite{RANDU}, which fails the spectral test
		\item \alert{\texttt{VEGAS}} \parencite{Lep78a, Lep21a} importance sampling Monte Carlo algorithm favored by physicists
		\item \alert{ACM} low discrepancy point generators \parencite{BraFox88,BraFoxNie92,HonHic00a}
		\item FinDer \parencite{PasTra95,FinDer} and BRODA \parencite{BRODA20a} targeting quantitative finance
		\item Korobov cubature and scrambled Sobol' generators in \alert{NAG} \parencite{NAG27} for decades		
		\item Scrambled Sobol' and Halton generators in \textcite{MAT9.13} since 2008
	\end{itemize}
\end{frame}

\begin{frame}{Selective History of MC\textbf{QMC} Software}
	\vspace{-6ex}
	\begin{itemize}
		\item Scrambled Sobol' and Halton generators in \textcite{MAT9.13} since 2008
		\item Scrambled Sobol' in SciPy \parencite{virtanen2020scipy} and PyTorch \parencite{paszke2019pytorch}
